---
output: word_document
params:
  survey: NA
  schedDepDate: NA
  schedArrDate: NA
  actDepDate: NA
  actArrDate: NA
  halfDate: NA
  personnel: !r NA
  depPort: NA
  halfPort: NA
  arrPort: NA
  objNum: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Not to be cited without reference to the Marine Laboratory, Aberdeen 

MRV Scotia 

Cruise `r params$survey`

***

## Dates

#### Departure  
**Scheduled Date:** `r params$schedDepDate`  
**Actual Date:** `r params$actDepDate`

#### Arrival  
**Scheduled Date:** `r params$schedArrDate`  
**Actual Date:** `r params$actArrDate`    

#### Half Landing  
**Date:** `r params$halfDate`

***

## Ports
**Departure Port:** `r params$depPort`  
**Half Landing Port:** `r params$halfPort`  
**Arrival Port:** `r params$arrPort` 

***

## Personnel
```{r, echo=FALSE, results = 'asis'} 
cat(unlist(params$personnel),sep="  \n")
```

## Objectives

`r params$objNum`


